Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-03-27 paper.tex
Add another test case: a cube

\subsection{A square}
Let's define a function $f(x, y) = \max(|x|, |y|)$. A set $f(x, y) \le T$ is a
square with side $2T$. The function $f$ is differentiable at all points where
$f(x, y) = T$ with exception of points $(-T, -T)$, $(-T, T)$, $(T, -T)$ and
$(T, T)$. The surface-surface correlation function for a square is equal to:
\begin{equation*}
  F_{ss}(x, y) = \left\{
  \begin{array}{ll}
    2 & \quad \max(|x|, |y|) < T \ \text{and}\ x\ne0, y\ne0 \\
    0 & \quad \max(|x|, |y|) > T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
this case the algorithm described in \cref{sec:algo} gives a correct result in
any point which is few pixels away from where $F_{ss}$ is undefined.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/fss-square.png}
  \caption[]{$F_{ss}$ function for a square with side $T$. The function is
    undefined along red segments. Its value is $2$ inside a shaded area and $0$
    outside.}
  \label{fig:fss-square}
\end{figure}

>>>>

\subsection{A square and a cube}
Define a function $f(\bm{x}) = \max\limits_i |x_i|$. A set $f(\bm{x}) \le T$
where $\bm{x} \in \mathbb{R}^2$ is a square with side $2T$. The function $f$ is
differentiable at all points where $f(\bm{x}) = T$ with exception of points
$(-T, -T)$, $(-T, T)$, $(T, -T)$ and $(T, T)$. The surface-surface correlation
function for a square is equal to:
\begin{equation*}
  F_{ss}(\bm{r}) = \left\{
  \begin{array}{ll}
    2 & \quad f(\bm{r}) < 2T \ \text{and}\ r_i \ne 0, \forall i \in \overline{1,2} \\
    0 & \quad f(\bm{r}) > 2T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
this case the algorithm described in \cref{sec:algo} gives a correct result in
any point which is few pixels away from where $F_{ss}$ is undefined.
\begin{figure}
  \centering
  \includegraphics[width=0.45\linewidth]{images/fss-square.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/fss-square-julia.png}
  \caption[]{$F_{ss}$ function for a square with side $T = 0.3$. On the left:
    Theoretical results. The function is undefined along red segments. Its value
    is $2$ inside a shaded area and $0$ outside. On the right: Calculation with
    the algorithm described in \cref{sec:algo}.}
  \label{fig:fss-square}
\end{figure}

A set $f(\bm{x}) \le T$ where $\bm{x} \in \mathbb{R}^3$ is a cube with the same
side $2T$.
The surface-surface-surface correlation function for this cube is equal to:
\begin{equation*}
  F_{sss}(\bm{r}) = \left\{
  \begin{array}{ll}
    2 & \quad f(\bm{r}) < 2T \ \text{and}\ r_i \ne 0, \forall i \in \overline{1,3} \\
    0 & \quad f(\bm{r}) > 2T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
This case is also handled good by the algorithm described in
\cref{sec:algo}. \textcolor{red}{Any picture/plot here?}.
